A Computational Account of Default-Mode Function\\ by Control Theory and Reinforcement Learning

### 2016-10-02 paper/paper.tex
synthesis I

\subsection{A Deep Q-learning for DMN function}
\textbf{XXX Put the diagrams and process charts here.}

>>>>

\subsection{Correspondence between DMN function and RL framework}
\textbf{XXX Put the diagrams and process charts here.}
\begin{itemize}
  \item The policy matrix represent the repertoire of possible actions
  on the world given a current state. It represents the probabilites of
  choosing actions to be executed in a certain situation.
  \item Given a state, the value function represents the estimated utility of
  being in that state, which is subjective to the agent. 
  For state s there is set of actions a.
  It provides a quantitative answer to the question:
  \"What state is desirable for a specific agent.\"
  For all actions being in one of the states s,
  the Q value function provides the subjective utility
  of executing a specific action.
  It provides a quantitative answer to the question:
  \"Which is the best action to take in the current situation.\"
  \item The DMN may subserve
  constant exploration of possible future actions and their
  cumulative outcomes. Implicit computation of future choices 
  provides an explanation for purposeful mind-wandering.
  \item hippocampus -> provides perturbed action-transition-state-reward samples
  as a block of "imagined", "hypothesized", "recalled" experience;
  the small variations in these experience blocks allow searching
  a larger space of parameters and possible experiences.
  In the absence of environmental input and feedback
  (e.g., mind-wandering or sleep) pseudo-experiencing possible
  future scenarios and action outcomes.

\end{itemize}
